ANON paper

### 2014-02-19 paper.tex
Lipsum for the introduction
Tor design introduction

	\section{Introduction}
		% The very first letter is a 2 line initial drop letter followed
		% by the rest of the first word in caps.
		% 
		% form to use if the first word consists of a single letter:
		% \IEEEPARstart{A}{demo} file is ....
		% 
		% form to use if you need the single drop letter followed by
		% normal text (unknown if ever used by IEEE):
		% \IEEEPARstart{A}{}demo file is ....
		% 
		% Some journals put the first two words in caps:
		% \IEEEPARstart{T}{his demo} file is ....
		% 
		% Here we have the typical use of a "T" for an initial drop letter
		% and "HIS" in caps to complete the first word.
		% You must have at least 2 lines in the paragraph with the drop letter
		% (should never be an issue)
		I wish you the best of success.

@@

		\bibitem{IEEEhowto:kopka}
			H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus 0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

	\section{Introduction}
		% The very first letter is a 2 line initial drop letter followed
		% by the rest of the first word in caps.
		% 
		% form to use if the first word consists of a single letter:
		% \IEEEPARstart{A}{demo} file is ....
		% 
		% form to use if you need the single drop letter followed by
		% normal text (unknown if ever used by IEEE):
		% \IEEEPARstart{A}{}demo file is ....
		% 
		% Some journals put the first two words in caps:
		% \IEEEPARstart{T}{his demo} file is ....
		% 
		% Here we have the typical use of a "T" for an initial drop letter
		% and "HIS" in caps to complete the first word.
		% You must have at least 2 lines in the paragraph with the drop letter
		% (should never be an issue)
		\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit. Nunc et elit nec metus ultrices faucibus. Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar. Sed et ipsum nunc. Quisque ac sem ut nunc tincidunt commodo. Cras at odio nibh. Pellentesque sodales ut tortor sed dictum. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.

	\section{Tor design}
		\label{sec:tor}
		The implementation of The Onion Router was first described by the U.S. Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{bib:goldschlag}.

		In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{bib:dingledine}.

		\subsection{Onion routing}

		\subsection{Directory servers}

		\subsection{Relay and exit nodes}

		\subsection{Circuit creation}

		\subsection{Disadvantages}

@@

		\bibitem{bib:goldschlag}
			David M. Goldschlag, Michael G. Reed, and Paul F. Syverson. "Hiding Routing Information", Workshop on Information Hiding, Cambridge, UK, May, 1996.

		\bibitem{bib:dingledine}
			Roger Dingledine, Nick Mathewson, Paul Syverson. "Tor: The Second-Generation Onion Router", 2002.
